Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-17 Documents/Paper/ms.tex
GalaxyField data figure
An abstract

\begin{document}
\maketitle
\abstract{Blah...
We demonstrate the techniques on a seemingly simple problem of detecting
sinusoidal signals in noise, which exhibits a phase transition.}

@@

>>>>

\begin{document}
\maketitle
\abstract{Many inference problems require us to infer the number $N$ of
objects in some region, along with their properties $\{\xx_i\}_{i=1}^N$,
from a dataset $\mathcal{D}$. These problems are typically solved using one
of the following two methods: i)
by executing a Monte Carlo algorithm (such as Nested Sampling) once for each
possible value of $N$,
and calculating the marginal likelihood or evidence as a function of $N$; or
ii) by doing a single run that allows the model dimension $N$ to change (such as
Markov Chain Monte Carlo with birth/death moves), and obtaining the posterior
for $N$ directly. In this paper we present a general approach to this problem
that uses trans-dimensional MCMC embedded {\it within} a Nested Sampling
algorithm, allowing us to explore the posterior distribution and calculate
the marginal likelihood (summed over $N$) even if the problem contains a phase
transition. We present two example problems, finding sinusoidal signals in
noisy data, and finding and measuring galaxies in a noisy astronomical image.}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.7]{galaxyfield_data.pdf}
\caption{The simulated data for the GalaxyField example.
\label{fig:galaxyfield_data}}
\end{center}
\end{figure}
